SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-07-26 scipy-1.0/paper.tex
Avoid starting a sentence with "And".
Fixes typo (hanker => Hankel)

The availability of a standard numerical array data structure in
Python led to a sudden, rapid growth in the number of scientific
packages available for solving common numeric problems.
A number of these packages were written by graduate students and
postdoctoral researchers to solve the very practical research problems
that they faced on a daily basis.  While they had access to and were
familiar with specialized (often commercial) systems, many found
it easier to implement the domain-specific functionality they needed
in a general purpose programming language.  And given Python's innate
ability to function as a systems language, controlling specialized or
custom-built hardware was also possible.

@@

    Special Functions (Bessel, hanker, Airy, etc.)
    Signal/Image Processing
    2D Plotting capabilities
    Integration
    ODE solvers
    Optimization (simplex, BFGS, Netwon-CG, etc.)
    Genetic Algorithms
    Numeric -> C++ expression compiler
    Parallel programming tools
    Splines and Interpolation
    And other stuff.
\end{verbatim}
\caption{Excerpt from SciPy 0.1 release announcement (typos included).}\label{fig:announce-0.1}
\end{figure}

>>>>

The availability of a standard numerical array data structure in
Python led to a sudden, rapid growth in the number of scientific
packages available for solving common numeric problems.
A number of these packages were written by graduate students and
postdoctoral researchers to solve the very practical research problems
that they faced on a daily basis.  While they had access to and were
familiar with specialized (often commercial) systems, many found
it easier to implement the domain-specific functionality they needed
in a general purpose programming language.  Given Python's innate
ability to function as a systems language, controlling specialized or
custom-built hardware was also possible.

@@

    Special Functions (Bessel, Hankel, Airy, etc.)
    Signal/Image Processing
    2D Plotting capabilities
    Integration
    ODE solvers
    Optimization (simplex, BFGS, Netwon-CG, etc.)
    Genetic Algorithms
    Numeric -> C++ expression compiler
    Parallel programming tools
    Splines and Interpolation
    And other stuff.
\end{verbatim}
\caption{Excerpt from SciPy 0.1 release announcement (typos included).}\label{fig:announce-0.1}
\end{figure}
